---
title: "Herbivory survey analysis"
output:
  html_document:
    df_print: paged
---

Load the Sun Shade header file:
```{r}
source("./_sun_shade_header.R")
```


Load the data:
```{r}
survey <- read.table(file="./data/source_site_traits/site_herbivory_final.txt",header=T)
```

### Plots

Plotting the data for A3 Fig. S1:
```{r fig.align='center', fig.height=2.5, fig.width=6, message=FALSE, warning=FALSE}
fS1a <- ggplot(survey,aes(x = stipples)) + geom_histogram(bins = 20) + facet_wrap(~ site_type) +
  theme_pth1() + xlab("stipples per leaf")
fS1b <- ggplot(survey,aes(x = mines)) + geom_histogram(bins = 20) + facet_wrap(~ site_type) +
  theme_pth1() + xlab("mines per leaf")

# Appendix 3: Fig. S1
# pdf(file = "./Appendix_S3/A3_figS1.pdf", width = 6, height = 2.5, onefile = F)
#   ggarrange(plotlist = list(fS1a, fS1b), nrow = 1, ncol = 2, labels = c("A","B"))
# dev.off()
ggarrange(plotlist = list(fS1a, fS1b), nrow = 1, ncol = 2, labels = c("A","B"))
```

Plot variance/mean ratios for stipple and mine data from herbivory survey (A3 Fig. S2):
```{r fig.align='center', fig.height=2.5, fig.width=3.5, message=FALSE, warning=FALSE, paged.print=FALSE}
survey3 <- dplyr::group_by(survey, site_type, site_id) %>% summarise(mu_stip = mean(stipples),
                                                                     var_stip = var(stipples),
                                                                     mu_mines = mean(mines),
                                                                     var_mines = var(mines))

fano1 <- ggplot(survey3, aes(y = var_stip/mu_stip, x = site_type)) +
  geom_point(size = 2.5, col = "gray40") +
  theme_pth1() + ggtitle("stipples") + theme(plot.title = element_text(size = 10, hjust = 0.5)) +
  geom_hline(yintercept = 1, col = "gray60", lty = 2) +
  xlab("") +
  ylab("variance / mean")

fano2 <- ggplot(survey3, aes(y = var_mines/mu_mines, x = site_type)) +
  geom_point(size = 2.5, col = "gray40") +
  theme_pth1() + ggtitle("mines") + theme(plot.title = element_text(size = 10, hjust = 0.5)) +
  geom_hline(yintercept = 1, col = "gray60", lty = 2) +
  xlab("") +
  ylab("variance / mean")

# pdf(file = "./Appendix_S3/A3_figS2.pdf", width = 4, height = 2.5)
#   ggarrange(plotlist = list(fano1, fano2), nrow = 1,ncol = 2, labels = c("A","B"))
# dev.off()

ggarrange(plotlist = list(fano1, fano2), nrow = 1,ncol = 2, labels = c("A","B"))
```


Plotting the data that went into Fig. 1A:
```{r, fig.height=2.5, fig.width=2.5, message=FALSE, warning=FALSE, fig.align='center'}
survey2 <- dplyr::group_by(survey, site_type, stem_id) %>% summarise(n_stips = sum(stipples), n_mines = sum(mines))

stip1 <- ggplot(survey2, aes(x = site_type, y = n_stips)) + 
  geom_jitter(width = 0.15, alpha = 0.3, col = "gray40") + 
  geom_boxplot(alpha = 0.5, col = "gray40") + theme_pth1() + 
  scale_y_continuous(limits = c(0,100), breaks = seq(0,100,20)) + xlab("") + ylab("stipples per plant")

mine1 <- ggplot(survey2, aes(x = site_type, y = n_mines)) + 
  geom_jitter(width = 0.15, alpha = 0.3, col = "gray40") + 
  geom_boxplot(alpha = 0.5, col = "gray40") + theme_pth1() + 
  scale_y_continuous(limits = c(0,20), breaks = seq(0,20,4)) + xlab("") + ylab("mines per plant")

ggarrange(plotlist = list(stip1, mine1))
```

### Models
#### Stipples

For illustrative purposes, below we run through the analyses described in Part 1 of Appendix S3, where we fit Poisson-only vs. ZI-Poisson and then factor-specific ZI parameters. We include fits estimated under NB as well. For these purposes, we removed the `area` term to improve model convergence of the habitat-specific ZI-Poisson model (below). In the section that follows, we re-fit and re-compare all models *including* this term.

Running Poisson-only and comparing to ZI-Poisson:
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
POIS.stip0 <- glmmTMB(stipples ~ site_type + (1|site_id) + (1|stem_id),
                     data = survey,
                     family = poisson)

POIS.stip1 <- glmmTMB(stipples ~ site_type + (1|site_id) + (1|stem_id),
                    zi = ~ 1,
                    data = survey,
                    family = poisson)

POIS.stip2 <- glmmTMB(stipples ~ site_type + (1|site_id) + (1|stem_id),
                      zi = ~ site_type,
                      data = survey,
                      family = poisson)
```

Generate simulations and make predictive distribution plots from MLE fits:
```{r}
set.seed(12345)

POIS.stip0.sim <- simulate(POIS.stip0,  nsim = 1000)
POIS.stip1.sim <- simulate(POIS.stip1,  nsim = 1000)
POIS.stip2.sim <- simulate(POIS.stip2,  nsim = 1000)

survey.stip.pp0 <- pp.plots(thesim = POIS.stip0.sim, thedat = survey, thefact = 'site_type', theresponse = 'stipples')
survey.stip.pp1 <- pp.plots(thesim = POIS.stip1.sim, thedat = survey, thefact = 'site_type', theresponse = 'stipples')
survey.stip.pp2 <- pp.plots(thesim = POIS.stip2.sim, thedat = survey, thefact = 'site_type', theresponse = 'stipples')
```

Generate plot for comparisons to include as A3 Fig. S3:
```{r, fig.height=2, fig.width=6, message=FALSE, warning=FALSE, fig.align='center'}
# pdf(file = "./Appendix_S3/POIS.stip0.pp.pdf", width = 6, height = 2, onefile = F)
#   survey.stip.pp0$plots
# dev.off()
survey.stip.pp0$plots
```

Calculate max(Y) distribution and p-value:
```{r, fig.height=2, fig.width=8, message=FALSE, warning=FALSE, fig.align='center'}
survey.stip.max0 <- pp.max(sim1 = POIS.stip0.sim, dat1 = survey, fact1 = 'site_type', response1 = 'stipples')
survey.stip.max1 <- pp.max(sim1 = POIS.stip1.sim, dat1 = survey, fact1 = 'site_type', response1 = 'stipples')
survey.stip.max2 <- pp.max(sim1 = POIS.stip2.sim, dat1 = survey, fact1 = 'site_type', response1 = 'stipples')

#ggarrange(plotlist = list(survey.stip.max0$plot,survey.stip.max1$plot,survey.stip.max2$plot),ncol = 3)
```

Generate A3 Fig. S4:
```{r, fig.height=2, fig.width=6, message=FALSE, warning=FALSE, fig.align='center'}
# pdf(file = "./Appendix_S3/POIS.stip1.pp.pdf", width = 6, height = 2, onefile = F)
#   survey.stip.pp1$plots
# dev.off()

survey.stip.pp1$plots
```

Generate A3 Fig. S5:
```{r, fig.height=2, fig.width=6, message=FALSE, warning=FALSE, fig.align='center'}
# pdf(file = "./Appendix_S3/POIS.stip2.pp.pdf", width = 6, height = 2, onefile = F)
#   survey.stip.pp2$plots
# dev.off()

survey.stip.pp2$plots
```

Try also to plot additional test statistic that might help reveal how Poisson fails to fit at the upper range, particularly for shaded sites (A3 Fig. S6):
```{r, fig.height=2, fig.width=3.25, message=FALSE, warning=FALSE, fig.align='center'}
POIS.stip0.max <- pp.max(sim1 = POIS.stip0.sim, dat1 = survey,
                         fact1 = 'site_type', response1 = 'stipples')
POIS.stip1.max <- pp.max(sim1 = POIS.stip1.sim, dat1 = survey,
                         fact1 = 'site_type', response1 = 'stipples')
POIS.stip2.max <- pp.max(sim1 = POIS.stip2.sim, dat1 = survey,
                         fact1 = 'site_type', response1 = 'stipples')
# ggarrange(plotlist = list(POIS.stip0.max$plot,POIS.stip1.max$plot,POIS.stip2.max$plot),ncol = 3)

# pdf(file = "./Appendix_S3/POIS.stip.2.max.pdf", width = 3.25, height = 2, onefile = F)
#   print(POIS.stip2.max$plot + xlab("max(Y)"))
# dev.off()
print(POIS.stip2.max$plot + xlab("max(Y)"))
```

Now run Negative Binomial models with and without ZI and dispersion terms:
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
ZINB.stip0  <- glmmTMB(stipples ~ site_type + (1|site_id) + (1|stem_id),
                     data = survey,
                     family = nbinom2)

ZINB.stip1  <- glmmTMB(stipples ~ site_type + (1|site_id) + (1|stem_id),
                     zi = ~ 1,
                     data = survey,
                     family = nbinom2)

ZINB.stip2  <- glmmTMB(stipples ~ site_type + (1|site_id) + (1|stem_id),
                     zi = ~ site_type,
                     data = survey,
                     family = nbinom2)

ZINB.stip3  <- glmmTMB(stipples ~ site_type + (1|site_id) + (1|stem_id),
                     zi = ~ 1,
                     dispformula = ~ 0 + site_type,
                     data = survey,
                     family = nbinom2)

ZINB.stip4  <- glmmTMB(stipples ~ site_type + (1|site_id) + (1|stem_id),
                     zi = ~ site_type,
                     dispformula = ~ 0 + site_type,
                     data = survey,
                     family = nbinom2)
# errors produced by these models above are normal.
# See https://cran.r-project.org/web/packages/glmmTMB/vignettes/troubleshooting.html
```

Output all model comparisons via $\text{AIC}_c$:
```{r}
AICs <- ICtab(POIS.stip0,POIS.stip1,POIS.stip2,ZINB.stip0,
              ZINB.stip1,ZINB.stip2,ZINB.stip3,ZINB.stip4, type = 'AICc')
print(AICs)
```

Output all model test statistics and generate table:
```{r}
AICs2 <- data.frame(model = attr(AICs, 'row.names'), dAICc = AICs[[1]], df = AICs[[2]])
# write.table(AICs2, file = "./model_output/AICs.txt",sep = "\t")
```

Generate simulations for sub-optimal ZINB models:
```{r, fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
survey.stip.sim0  <- simulate(ZINB.stip0,  nsim = 1000)
survey.stip.sim1  <- simulate(ZINB.stip1,  nsim = 1000)
survey.stip.sim2  <- simulate(ZINB.stip2,  nsim = 1000)
survey.stip.sim4  <- simulate(ZINB.stip4,  nsim = 1000)

# calcualte pp.plots for each:
ZINB.pp0 <- pp.plots(thesim = survey.stip.sim0, thedat = survey,
                     thefact = 'site_type', theresponse = 'stipples')
ZINB.pp1 <- pp.plots(thesim = survey.stip.sim1, thedat = survey,
                     thefact = 'site_type', theresponse = 'stipples')
ZINB.pp2 <- pp.plots(thesim = survey.stip.sim2, thedat = survey,
                     thefact = 'site_type', theresponse = 'stipples')
ZINB.pp4 <- pp.plots(thesim = survey.stip.sim4, thedat = survey,
                     thefact = 'site_type', theresponse = 'stipples')

#ggarrange(plotlist = list(ZINB.pp0$plots,ZINB.pp1$plots,ZINB.pp2$plots,ZINB.pp4$plots))
```

Now for the maximum values:
```{r, fig.height=4, fig.width=6, message=FALSE, warning=FALSE, fig.align='center'}
ZINB.pp.max0 <- pp.max(sim1 = survey.stip.sim0, dat1 = survey,
                       fact1 = 'site_type', response1 = 'stipples')
ZINB.pp.max1 <- pp.max(sim1 = survey.stip.sim1, dat1 = survey,
                       fact1 = 'site_type', response1 = 'stipples')
ZINB.pp.max2 <- pp.max(sim1 = survey.stip.sim2, dat1 = survey,
                       fact1 = 'site_type', response1 = 'stipples')
ZINB.pp.max4 <- pp.max(sim1 = survey.stip.sim4, dat1 = survey,
                       fact1 = 'site_type', response1 = 'stipples')

#ggarrange(plotlist = list(ZINB.pp.max0$plot,ZINB.pp.max1$plot,ZINB.pp.max2$plot,ZINB.pp.max4$plot))
```

Output coefficient estimates for best model:
```{r}
survey.stip.bm <- ZINB.stip3
ci_stips <- confint(survey.stip.bm)
coef_stips <- do.call(rbind,summary(survey.stip.bm)$coef)
round(ci_stips,2)
```

Simulate best stipple model:
```{r}
set.seed(12345)
survey.stip.sim  <- simulate(survey.stip.bm,  nsim = 1000)
```

Predictive model check for $p(0)_i$ and $\mu_i$:
```{r, fig.height=2, fig.width=6, message=FALSE, warning=FALSE, fig.align='center'}
survey.stip.pp <- pp.plots(thesim = survey.stip.sim, thedat = survey, thefact = 'site_type', theresponse = 'stipples')

# pdf(file = "./Appendix_S3/survey_stip_pp.pdf", width = 6, height = 2, onefile = F)
#   print(survey.stip.pp$plots)
# dev.off()

print(survey.stip.pp$plots)
```

Additional check on max(Y) to see that NB fixed problem for shade sites:
```{r, fig.height=2, fig.width=3.25, message=FALSE, warning=FALSE, fig.align='center'}
survey.stip.max <- pp.max(sim1 = survey.stip.sim, dat1 = survey, fact1 = 'site_type', response1 = 'stipples')

# pdf(file = "./Appendix_S3/survey_stip_max.pdf", width = 3.25, height = 2, onefile = F)
#   print(survey.stip.max$plot)
# dev.off()

print(survey.stip.max$plot)
```

Print summary of test statistics:
```{r}
print(survey.stip.pp$means)
```

```{r}
print(survey.stip.pp$p0)
```

```{r}
print(survey.stip.pp$intensity)
```

Combined plot output of best ZINB model (A3 Fig. S7):
```{r, fig.height=2, fig.width=8, message=FALSE, warning=FALSE, fig.align='center'}
survey.stip.max$plot <- survey.stip.max$plot + xlab("max(Y)")
# pdf(file = "./Appendix_S3/pp_stips_best_mod.pdf", width = 8, height = 2, onefile = F)
#   ggarrange(plotlist = list(survey.stip.pp$plots,survey.stip.max$plot), labels = c('','C'), align = 'hv', widths = c(2.15,1))
# dev.off()
ggarrange(plotlist = list(survey.stip.pp$plots,survey.stip.max$plot), labels = c('','C'), align = 'hv', widths = c(2.15,1))
```

#### Re-fitting all models with `area` term

Including the `area` term results in convergence issues with the habitat-specific ZI-Poisson model (`POIS.stip2`) but does not affect the optimisation of any of the other models. Below we report model comparisons among all of the above models re-fit with `area` except `POIS.stip2`.

First, re-fit:
```{r, message=FALSE, warning=FALSE}
# re-fit all models with area term:
survey <- survey[complete.cases(survey),] # remove all rows with any 'NA' elements (excludes one additional row with NA leaf area)

POIS.stip0b <- glmmTMB(stipples ~ area + site_type + (1|site_id) + (1|stem_id),
                     data = survey,
                     family = poisson)

POIS.stip1b <- glmmTMB(stipples ~ area + site_type + (1|site_id) + (1|stem_id),
                    zi = ~ 1,
                    data = survey,
                    family = poisson)
# errors produced by these models above are normal.
# See https://cran.r-project.org/web/packages/glmmTMB/vignettes/troubleshooting.html

POIS.stip2b <- glmmTMB(stipples ~ area + site_type + (1|site_id) + (1|stem_id),
                      zi = ~ site_type,
                      data = survey,
                      family = poisson) # this model has convergence problems!

## ZI-Negative Binomial models
ZINB.stip0b  <- glmmTMB(stipples ~ area + site_type + (1|site_id) + (1|stem_id),
                     data = survey,
                     family = nbinom2)

ZINB.stip1b  <- glmmTMB(stipples ~ area + site_type + (1|site_id) + (1|stem_id),
                     zi = ~ 1,
                     data = survey,
                     family = nbinom2)

ZINB.stip2b  <- glmmTMB(stipples ~ area + site_type + (1|site_id) + (1|stem_id),
                     zi = ~ site_type,
                     data = survey,
                     family = nbinom2)

ZINB.stip3b  <- glmmTMB(stipples ~ area + site_type + (1|site_id) + (1|stem_id),
                     zi = ~ 1,
                     dispformula = ~ 0 + site_type,
                     data = survey,
                     family = nbinom2)

ZINB.stip4b  <- glmmTMB(stipples ~ area + site_type + (1|site_id) + (1|stem_id),
                     zi = ~ site_type,
                     dispformula = ~ 0 + site_type,
                     data = survey,
                     family = nbinom2)
```

Re-running model comparisons via $\text{AIC}_c$:
```{r}
AICsb <- ICtab(POIS.stip0b,POIS.stip1b,POIS.stip2b,
               ZINB.stip0b,ZINB.stip1b,ZINB.stip2b,ZINB.stip3b,ZINB.stip4b, type = 'AICc')
print(AICsb)
```

Output coefficient estimates for best model (still `ZINB.stip3`, now labeled `ZINB.stip3b` with `area` term):
```{r}
survey.stip.bm_2 <- ZINB.stip3b
ci_stips <- confint(survey.stip.bm_2)
coef_stips <- do.call(rbind,summary(survey.stip.bm_2)$coef)
round(ci_stips,2)
```

Simulate best model and output test statistics:
```{r}
set.seed(12345)
survey.stip.sim_2  <- simulate(survey.stip.bm_2,  nsim = 1000)
survey.stip.pp_2 <- pp.plots(thesim = survey.stip.sim_2, thedat = survey, thefact = 'site_type', theresponse = 'stipples')
survey.stip.max_2 <- pp.max(sim1 = survey.stip.sim_2, dat1 = survey, fact1 = 'site_type', response1 = 'stipples')
```

Plot predictive distributions of test statistics:
```{r fig.height=2, fig.width=8, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align='center'}
survey.stip.max_2$plot <- survey.stip.max_2$plot + xlab("max(Y)")
ggarrange(plotlist = list(survey.stip.pp_2$plots,survey.stip.max_2$plot),
          labels = c('','C'), align = 'hv', widths = c(2.15,1))
```

Generate predicted responses for main text:
```{r}
print(survey.stip.pp_2$means)
```


```{r}
print(survey.stip.pp_2$p0)
```

```{r}
print(survey.stip.pp_2$intensity)
```

Note that intensity was not reported in text. This is the average stipple count *given that the leaf was damaged*, rather than the average stipple number across all sampled leaves (i.e., including zeros).


### Models of Leaf mines from herbivory survey

Run the models, *with* leaf area in all cases:

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
## POISSON MODELS
POIS.mines0  <- glmmTMB(mines ~ site_type + area + (1|site_id) + (1|stem_id),
                     #zi = ~1,
                     data = survey,
                     family = poisson)

POIS.mines1  <- glmmTMB(mines ~ site_type + area + (1|site_id) + (1|stem_id),
                     zi = ~1,
                     data = survey,
                     family = poisson)

POIS.mines2  <- glmmTMB(mines ~ site_type + area + (1|site_id) + (1|stem_id),
                     zi = ~site_type,
                     data = survey,
                     family = poisson)

## NEGATIVE BINOMIAL MODELS
ZINB.mines0  <- glmmTMB(mines ~ site_type + area + (1|site_id) + (1|stem_id),
                     #zi = ~1,
                     #dispformula = ~1,
                     data = survey,
                     family = nbinom2)

ZINB.mines1  <- glmmTMB(mines ~ site_type + area + (1|site_id) + (1|stem_id),
                     zi = ~1,
                     #dispformula = ~1,
                     data = survey,
                     family = nbinom2)

ZINB.mines2  <- glmmTMB(mines ~ site_type + area + (1|site_id) + (1|stem_id),
                     zi = ~ site_type,
                     #dispformula = ~0 + site_type,
                     data = survey,
                     family = nbinom2)

ZINB.mines3  <- glmmTMB(mines ~ site_type + area + (1|site_id) + (1|stem_id),
                     zi = ~ 1,
                     dispformula = ~ site_type,
                     data = survey,
                     family = nbinom2)

ZINB.mines4  <- glmmTMB(mines ~ site_type + area + (1|site_id) + (1|stem_id),
                     zi = ~ site_type,
                     dispformula = ~ site_type,
                     data = survey,
                     family = nbinom2) # convergence problems; not considered further.
```

Output model comparisons via $\text{AIC}_c$:
```{r}
ICtab(POIS.mines0,POIS.mines1,POIS.mines2,
      ZINB.mines0,ZINB.mines1,ZINB.mines2,ZINB.mines3,ZINB.mines4, type = 'AICc')
```

Output coefficient estimate for best model:
```{r}
# best model
survey.mine.bm <- ZINB.mines3
ci_mines <- confint(survey.mine.bm)
coef_mines <- do.call(rbind,summary(survey.mine.bm)$coef)
round(ci_mines,2)
```

Simulate best model for mines:
```{r}
set.seed(12345)
survey.mine.sim  <- simulate(survey.mine.bm,  nsim = 1000)
```

Predictive model check for $p(0)_i$ and $\mu_i$:
```{r fig.height=2, fig.width=8, message=FALSE, warning=FALSE, fig.align='center'}
survey.mine.pp <- pp.plots(thesim = survey.mine.sim, thedat = survey,
                           thefact = 'site_type', theresponse = 'mines')
survey.mine.max <- pp.max(sim1 = survey.mine.sim, dat1 = survey,
                          fact1 = 'site_type', response1 = 'mines')

survey.mine.max$plot <- survey.mine.max$plot + xlab("max(Y)")

ggarrange(plotlist = list(survey.mine.pp$plots,survey.mine.max$plot),
          labels = c('','C'), align = 'hv', widths = c(2.15,1))
```

Predictive model checks for best-ranked Poisson (but worse than ZINB via AICc) model:
```{r fig.height=2, fig.width=8, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align='center'}
survey.mine.sim.pois  <- simulate(POIS.mines2,  nsim = 1000)
survey.mine.pp.pois <- pp.plots(thesim = survey.mine.sim.pois, thedat = survey,
                                thefact = 'site_type', theresponse = 'mines')
survey.mine.max.pois <- pp.max(sim1 = survey.mine.sim.pois, dat1 = survey,
                               fact1 = 'site_type', response1 = 'mines')

survey.mine.max.pois$plot <- survey.mine.max.pois$plot + xlab("max(Y)")

ggarrange(plotlist = list(survey.mine.pp.pois$plots,survey.mine.max.pois$plot),
          labels = c('','C'), align = 'hv', widths = c(2.15,1))
```

In many ways, the ZI-Poisson (ZIP) model (`POIS.mines2`) fits as well if not slightly better via max(Y) than the best ZINB model (`ZINB.mines3`) (for sun habitats, $p_{T_{max}}^{ZIP} = 0.945; p_{T_{max}}^{ZINB} = 0.986$). However, judged by $\text{AIC}_c$, the ZINB version with habitat-specific dispersion is a better overall model ($\Delta \text{AIC}_c = -12.6$). Both models produce very similar predicted responses in terms of means and prevalence. Let's directly compare, first with the best ZINB model:
```{r}
print(survey.mine.pp$means)
```

```{r}
print(survey.mine.pp$p0)
```

Now for the ZIP model:
```{r}
print(survey.mine.pp.pois$means)
```

```{r}
print(survey.mine.pp.pois$p0)
```

In the end, the differences are operationally indistinguishable for the main response variables we are interested in (prevalence and overall mean abundance of damage). Thus, we will defer to the $\Delta \text{AIC}_c$ result for determining which model to report in Table 1 of the main text (`ZINB.mines3`).

### Outputting model coefficients

Below we output model coefficients reported in Table 1 of the main text:

```{r}
OUTDIR <- "./model_output/"
write.table(round(ci_stips,2), file = paste0(OUTDIR,"survey_stips.txt"), sep = '\t')
write.table(round(ci_mines,2), file = paste0(OUTDIR,"survey_mines.txt"), sep = '\t')
write.table(round(coef_stips,4), file = paste0(OUTDIR,"survey_stips_coef.txt"), sep = '\t')
write.table(round(coef_mines,4), file = paste0(OUTDIR,"survey_mines_coef.txt"), sep = '\t')
```

#### Output session info

```{r}
sessionInfo()
```

